\section{Methodology}\label{sec:methodology}

This section describes the components of our agentic fraud detection system.

\subsection{Data Collection and Annotation}

We collected fraud-related data from social media platforms where people share their scam experiences. The data collection process involved two main steps.

First, we scraped posts from social media using targeted keywords related to common fraud types such as investment scams, phishing, and payment fraud. The scraping targeted posts from the past several months to capture recent fraud patterns. We collected post content, timestamps, and user interactions.

Second, we used large language models to automatically label the collected data. The LLM was prompted as an expert fraud analyst to identify whether each post described actual fraud using the post and the comments of that post, extract the type of fraud if present, and note payment methods used. The LLM also provided confidence scores for its predictions. Posts with low confidence scores were filtered out to ensure data quality.

The resulting dataset contains labeled examples of both fraudulent and normal transactions. This labeled data serves as the foundation for training our detection models.

\subsection{Data Augmentation using CTGAN}

Fraud detection datasets typically have far more normal transactions than fraudulent ones. This class imbalance makes it difficult for models to learn to detect fraud effectively. We address this using CTGAN, a generative adversarial network designed for tabular data \cite{xu2019ctgan}.

CTGAN consists of two neural networks that work against each other. The generator creates synthetic data that looks real, while the discriminator tries to distinguish between real and fake data. Through training, the generator learns to produce realistic samples that match the statistical properties of the original data.

We trained CTGAN on our minority class examples, which in this case are the normal transactions. The trained model generates new synthetic examples of normal transactions. These synthetic examples help balance the dataset, giving the model more examples to learn from.

To ensure the quality of synthetic data, we validated it using statistical tests. We compared the distribution of synthetic data with real data using Jensen-Shannon Divergence to ensure the generated samples maintain the same statistical properties as the original dataset.

\subsection{Adversarial Training}

Fraudsters can deliberately try to trick detection systems by modifying their transaction patterns. To make our model robust against such attacks, we use adversarial training \cite{madry2018adversarial}.

Adversarial training involves adding small perturbations to the input data during training. These perturbations are calculated to maximize the model's loss, creating worst-case examples. By training on these adversarial examples, the model learns to handle attacks and maintains good performance even when inputs are modified \cite{goodfellow2014gan}.

In our implementation, we add small random noise to the training data to simulate potential attacks. The model learns to correctly classify both clean and perturbed examples. This process improves the model's robustness without significantly affecting its performance on normal transactions.

We test the model's robustness by measuring performance degradation under different attack strengths. Our experiments show that adversarial training helps the model maintain high accuracy even when facing adversarial perturbations.

\subsection{MAPE-K Agent Architecture}

The core of our system is the MAPE-K architecture, which enables autonomous adaptation. MAPE-K stands for Monitor, Analyze, Plan, Execute, and Knowledge. This architecture was originally proposed by IBM for autonomic computing systems \cite{ibm2005autonomic, kephart2003vision}.

Our implementation follows: Monitor $\rightarrow$ Analyze $\rightarrow$ Decision $\rightarrow$ Plan $\rightarrow$ Execute with active Knowledge base. The system includes:

\begin{enumerate}
  \item \textbf{Monitor}: DriftAgent + FeatureExtractionAgent - Detects concept drift using PSI/KS tests and extracts fraud features
  \item \textbf{Analyze}: RuleBasedScoringAgent + PatternLearningAgent - Rule-based scoring and pattern classification
  \item \textbf{Decision}: LLM Decision Agent (Llama 3) - Contextual decision-making with reasoning
  \item \textbf{Plan}: TrainingAgent - Model training with adversarial training
  \item \textbf{Execute}: BalanceAgent - CTGAN balancing and deployment
  \item \textbf{Knowledge}: SQLite Knowledge Store - Persistent memory with 8 tables
\end{enumerate}

\sububsection{Feature Extraction Agent}

The Feature Extraction Agent parses fraud labels, key features, and psychological tactics from transaction data. It produces a semantic profile combining labels and behavioral features into a compact fraud signature. Active fraud labels include credential\_phishing, social\_authority\_scam, social\_urgency\_scam, and others. Psychological tactics include urgency, fear, authority, and reward.

\sububsection{Rule-Based Scoring Agent}

The Rule-Based Scoring Agent applies transparent weighted rules:
\begin{itemize}
  \item credential\_phishing: +0.25
  \item social\_authority\_scam: +0.25  
  \item urgency: +0.15
  \item fear: +0.15
\end{itemize}
The final score is clamped between 0 and 1, providing explainable fraud estimation.

\sububsection{Pattern Learning Agent}

The Pattern Learning Agent maps fraud indicators to known or emerging patterns:
\begin{itemize}
  \item PHISHING: credential\_phishing detected
  \item SOCIAL\_ENGINEERING: authority + fear detected
  \item HYBRID: multiple labels combined
\end{itemize}
If a pattern appears fewer than 3 times historically, it's marked as emerging.

\sububsection{LLM Decision Agent}

The Decision Agent uses Ollama Llama 3 for contextual reasoning. Given system state (drift, metrics, prior F1), the LLM decides: deploy, retrain\_L2, retrain\_new\_strategy, or stop. This replaces hardcoded threshold rules with adaptive reasoning.

\sububsection{Knowledge Store}

The Knowledge Store is SQLite-based with 8 tables:
\begin{itemize}
  \item transactions: Raw transaction data
  \item predictions: Model predictions
  \item reasoning: LLM reasoning traces
  \item patterns: Learned fraud patterns
  \item adversarial\_variants: Adversarial test results
  \item execution\_logs: Action history
  \item feedback: Human feedback for continuous learning
  \item metrics: Performance metrics
\end{itemize}

\subsubsection{Feedback and Learning}

The Feedback Agent processes human corrections to improve future decisions. When incorrect predictions are flagged, it triggers retraining review. The system tracks learning improvement rate to measure if feedback enhances decision quality.

\sububsection{Agentic Performance Metrics}

We measure:
\begin{itemize}
  \item F1-score and ROC-AUC (core classification)
  \item PR-AUC (for imbalanced data)
  \item Adversarial accuracy (robustness under attack)
  \item Planning accuracy (correct action selection)
  \item Drift detection rate (PSI, KS thresholds)
\end{itemize}

\sububsection{Feedback Loops}

Our system implements five feedback loops:
\begin{itemize}
  \item L1: Decision $\rightarrow$ Balance (re-balance data)
  \item L2: Decision $\rightarrow$ Training (change strategy)
  \item L3: Training $\rightarrow$ Monitor (re-check drift)
  \item L4: Supervisor (iteration cap, convergence)
  \item L5: Decision $\rightarrow$ Knowledge (store results)
\end{itemize}

\sububsection{Supervisor}

The Supervisor component provides oversight with three rules: Max Iterations (stop after 3 retry attempts), Convergence (stop early if $\Delta$F1 $<$ 0.01), and Unstable Override (stop if F1 $<$ 0.3 after 2 iterations).

When drift is detected or metrics are poor, the system automatically triggers a correction cycle. The LLM decision node determines whether to deploy existing model or trigger retraining.