\section{Results}\label{sec:results}

This section presents the experimental results for our agentic fraud detection system. We evaluated performance across multiple dimensions including classification accuracy, robustness, drift detection, and data quality.

\subsection{Classification Performance}

Our system achieves strong results on the fraud detection task. The model reached an F1 score of 0.9911, indicating high precision and recall balance. The ROC-AUC score of 0.9966 shows excellent ability to distinguish between fraud and normal transactions across different thresholds.

The precision and recall both reached 0.9911, meaning the model correctly identifies fraudulent transactions while keeping false alarms low. The false positive rate was 7.79 percent, which is acceptable for practical deployment where catching fraud is more important than slightly annoying users with occasional false alarms.

These results demonstrate that combining CTGAN data augmentation with adversarial training produces an effective fraud detector that performs well on real-world data.

\subsection{Robustness under Adversarial Attacks}

We tested how well the model handles adversarial perturbations. We evaluated performance at different attack strengths, ranging from zero to 0.30 perturbation levels.

The model maintained strong performance even under attack. At the highest perturbation level of 0.30, the F1 score remained at 0.9803, only dropping slightly from the clean F1 of 0.9911. This shows the model is robust against attempts to trick it by modifying transaction features.

The overall robustness score was 98.34 percent, calculated as the ratio of average F1 under attack to clean F1. This far exceeds our target threshold of 60 percent. The attack success rate, measuring how much performance degrades under attack, was only 1.09 percent.

These results demonstrate that adversarial training effectively prepares the model to handle evasion attempts. Even when fraudsters try to manipulate their transactions to bypass detection, the model maintains high accuracy.

\subsection{Drift Detection and Adaptation}

We tested the system's ability to detect and adapt to concept drift. During one of our experimental runs, significant drift was detected with a PSI value of 0.22, which exceeded our threshold of 0.20. The KS statistic also showed drift at 0.09.

When drift was detected, the system automatically triggered the retraining cycle. The Balance Agent first ensured the dataset was properly balanced using CTGAN. The Training Agent then retraines the model with fresh data and adversarial examples. The Evaluation Agent verified that the retrained model met performance thresholds.

After retraining, the system successfully recovered. The new model achieved F1 score of 0.92, showing the system can adapt to changing fraud patterns. The drift metrics returned to normal levels, confirming the adaptation was successful.

This demonstrates the practical value of the MAPE-K architecture. The system can detect problems on its own and take corrective action without human intervention.

\subsection{Data Quality Validation}

We validated the quality of synthetic data generated by CTGAN using Jensen-Shannon Divergence. The JSD score was 0.1291, which is below our threshold of 0.20. This confirms the synthetic data maintains the statistical properties of the original dataset.

We also performed chi-squared tests on categorical features and Kolmogorov-Smirnov tests on numerical features. The categorical test passed for 100 percent of features. The numerical test passed for 97.1 percent of features. These results confirm the synthetic data is realistic and suitable for training.

To find the optimal amount of synthetic data, we experimented with different quantities. The best results were achieved with around 700 synthetic samples. Adding more than this did not improve performance and in some cases hurt it due to noise introduction.

\subsection{Comparison with Baseline}

We compared our full system against several baselines to understand the contribution of each component.

A baseline model without CTGAN or adversarial training achieved F1 of 0.74 under drift conditions. Adding CTGAN improved this to 0.87. Adding adversarial training on top of CTGAN achieved F1 of 0.92 even under drift.

The MAPE-K architecture provides additional value by enabling automatic adaptation. When drift occurs, the baseline without MAPE-K would require manual intervention to retrain. Our system handles this automatically.

The combination of all four components produces the best results and enables a truly autonomous fraud detection system.